% LaTeX Resume Pandoc Template jb2resume.latex
%
% Copyright (c) 2016-2017, John Bokma
% Based on Jason Blevins' LaTeX CV Template;
%       http://jblevins.org/projects/cv-template/
%
% GitHub: https://github.com/john-bokma/resume-pandoc

\documentclass[10pt,letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{underscore}
\usepackage[parfill]{parskip}
\usepackage{lmodern}
\usepackage[svgnames]{xcolor}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% Your name on the resume
\def\name{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor=blue,
  linkcolor=magenta,  
  pdfauthor = {\name},
  pdfkeywords = {},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 9.0in},
  left=1.0in,
  top=1.0in
}

% Fix  for "! Undefined control sequence. <recently read> \tightlist",
% see: https://github.com/osener/markup.rocks/issues/4
% I have this issue with Pandoc 1.17.2
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% Page number is top right, and it is possible to control the rest of
% the header.
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Section numbers or not (default)
\setcounter{secnumdepth}{0}

% By putting an empty \item[] at the start of the list, the list
% starts on a new line.
\setlist[itemize]{leftmargin=1em,label={--},before=\item[]}

\setlist[description]{leftmargin=0em, style=sameline}

% Don't use monospace font for URLs
\urlstyle{same}

\begin{document}

% Place name at left
{\huge \name}

\bigskip


\hypertarget{raphael-amiard}{%
\section{Raphael Amiard}\label{raphael-amiard}}

Senior compiler and language frontend engineer

\begin{itemize}
\tightlist
\item
  E-mail:\href{mailto:raph.amiard@gmail.com}{\nolinkurl{raph.amiard@gmail.com}}
\item
  Website:\href{https://raph-amiard.github.io}{raph-amiard.github.io}
\end{itemize}

I am a language geek. My passion is in compilers and language design. I
developped several interpreters, worked on a few compilers, and designed
or helped design several computer languages.

I'm fluent in many computer languages, and can learn new ones easily.

\hypertarget{work-experience}{%
\subsection{Work experience}\label{work-experience}}

\hypertarget{adacore}{%
\subsubsection{\texorpdfstring{\textbf{2013-2023} -
\href{https://www.adacore.com/}{AdaCore}}{2013-2023 - AdaCore}}\label{adacore}}

Compiler/language front-end engineer. Lead developper/team manager

\begin{itemize}
\item
  Lead developper/manager of the
  \href{https://github.com/AdaCore/libadalang}{Libadalang} \&
  \href{https://github.com/AdaCore/libadalang}{Langkit} projects.

  \begin{itemize}
  \tightlist
  \item
    Ada front-end which powers a big portion of the Ada tools at
    AdaCore, including our IDEs, code style checkers, and static
    analysis tools
  \item
    I originally started the projects on my own, closely followed by a
    colleague
  \item
    10 years later I manage a 5 developper team driving the
    development/maintenance/R\&D around those projects.
  \item
    Presentation about Langkit at FOSDEM 2018:
    \href{https://archive.fosdem.org/2018/schedule/event/code_reviving_the_meta_compiler_dream/}{Langkit:
    source code analyzers for the masses}
  \item
    Presentation about Libadalang at FOSDEM 2018:
    \href{https://archive.fosdem.org/2018/schedule/event/ada_tooling/}{Easy
    Ada Tooling with Libadalang}
  \end{itemize}
\item
  Lead developer \& manager of
  \href{https://github.com/AdaCore/langkit-query-language}{LKQL}, a
  query language for syntax trees.

  \begin{itemize}
  \tightlist
  \item
    Powers the
    \href{https://www.adacore.com/static-analysis/gnatcheck}{GNATcheck}
    style checker
  \item
    Allows the quick \& easy definition of checkers from syntax patterns
  \end{itemize}
\item
  Member of the Ada Rapporteur Group (group in charge of the
  standardization of the Ada language) since 2015.
\item
  Lead \href{https://github.com/AdaCore/ada-spark-rfcs/}{language design
  at AdaCore}.

  \begin{itemize}
  \tightlist
  \item
    Role: Leading \& coordinating the working groups around language
    evolutions.
  \item
    Led working group on
    \href{https://github.com/AdaCore/ada-spark-rfcs/pull/50}{pattern
    matching}
  \item
    Leading working group on
    \href{https://github.com/AdaCore/ada-spark-rfcs/pull/103}{improved
    generics}
  \end{itemize}
\item
  Initial developper (together with
  \href{https://github.com/pmderodat}{@derodat}) of the
  \href{https://github.com/AdaCore/gnat-llvm}{GNAT-llvm} project, a
  middle-end for the GNAT compiler to emit LLVM IR.
\item
  Co-authored and presented
  \href{https://dblp.org/pid/170/1454.html}{Application of SMT in a
  Meta-Compiler: A Logic DSL for Specifying Type Systems}, together with
  \href{https://www.linkedin.com/in/romain-beguet-88719a130/}{Romain
  Beguet}.
\item
  Co-wrote the
  \href{https://learn.adacore.com/pdf_books/courses/intro-to-ada.pdf}{Introduction
  to Ada} course/book.
\end{itemize}

\hypertarget{epita}{%
\subsubsection{\texorpdfstring{\textbf{2016-2023} -
\href{https://www.epita.fr/en/}{EPITA}}{2016-2023 - EPITA}}\label{epita}}

\begin{itemize}
\tightlist
\item
  Teacher at EPITA for the \textbf{GISTRE} (Génie Informatique des
  systèmes temps réel et embarqués) major.
\item
  Teaching
  \href{https://en.wikipedia.org/wiki/Ada_(programming_language)}{Ada},
  realtime/embedded programming, and
  \href{https://www.rust-lang.org/}{Rust} since

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \setcounter{enumi}{2019}
  \tightlist
  \item
  \end{enumerate}
\end{itemize}

\hypertarget{google-summer-of-code}{%
\subsubsection{\texorpdfstring{\textbf{2012} -
\href{https://summerofcode.withgoogle.com/}{Google Summer of
Code}:}{2012 - Google Summer of Code:}}\label{google-summer-of-code}}

\begin{itemize}
\tightlist
\item
  Modularisation of the ClojureScript compiler's backend (Clojure to
  Javascript compiler).
\item
  \href{https://github.com/raph-amiard/clojurescript-lua}{Development of
  a new Lua backend}.
\end{itemize}

\hypertarget{freelance-web-developper}{%
\subsubsection{\texorpdfstring{\textbf{2010-2011} - Freelance web
developper:}{2010-2011 - Freelance web developper:}}\label{freelance-web-developper}}

\begin{itemize}
\item
  Freelance for \textbf{e-loue} -- Python -- Django development.
  Development of a dynamic application backed by a rest API, using
  Django/Tastypie and backbone.js.
\item
  Four months internship at \textbf{Paperblog} -- news and information
  website, using Python -- Django Infrastructure and front-end
  development. Web scraping engine using Coffeescript.
\end{itemize}

\hypertarget{education}{%
\subsection{Education}\label{education}}

\begin{itemize}
\tightlist
\item
  \textbf{2010-2012} Master « Distributed systems and applications » -
  Pierre et Marie Curie (Paris VI) university
\item
  \textbf{2008-2010} Licence in Computer Science -- first class - Pierre
  et Marie Curie (Paris VI) university
\item
  \textbf{2003-2008} Master in Human Sciences, Sociology major - René
  Descartes (Paris V) university
\end{itemize}

\hypertarget{others}{%
\subsection{Others}\label{others}}

\hypertarget{personal-projects}{%
\subsubsection{Personal projects}\label{personal-projects}}

\begin{itemize}
\item
  \href{https://github.com/raph-amiard/CamllVM}{Camllvm} - An LLVM based
  bytecode compiler for OCaml.
\item
  \href{https://github.com/raph-amiard/ada-synth-lib}{ada-synth-lib} - A
  very simple sound/music synthesis library.
\item
  \href{https://github.com/raph-amiard/Lune}{lune} - A small functional
  language with Hindley-Milner type inference and typeclasses
\end{itemize}

\hypertarget{personal-interests}{%
\subsubsection{Personal interests}\label{personal-interests}}

\begin{itemize}
\tightlist
\item
  Electronic music creator and lover. Released several projects in
  digital or vinyl over the years.
\item
  Co-created the https://excellentchoix.bandcamp.com/ music label
\end{itemize}

\end{document}
